---
title: "Practice Exam 1"
tutorial:
  id: "isds_pexam1"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  This proficiency exam covers Preface - Chapter 4.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ISDStutorials)
library(gradethis)

library(stat202exams)
#conflicted::conflict_prefer_all("stat202exams", "learnr")
conflicted::conflict_prefer_all("stat202exams", "ISDStutorials")

knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
options(tutorial.event_recorder = ISDStutorials::isds_recorder)
```



```{r isds-header}
# student name
question_blank("Name: ___",
                            answer_fn(function(value){
                              if (length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
          style = "notes_question",
          correct = paste0(fontawesome::fa("check") ),
          incorrect = paste0(fontawesome::fa("xmark") ),
          allow_retry = FALSE )
# have name, grade button, and print button on same line
bootstrapPage(
     div(style="display:inline-block", print_ui("Print") )
)
```


## Instructions

You have 50 minutes to complete this exam. The exam covers the material learned from Preface - Chapter 4 and is open note, open book.

Once you are finished:

-   Make sure every question/exercise has been submitted.
-   Click the 'pdf' button to save the document as a pdf, you must have the exam open in a browser window for this button to work.
-   Submit the completed pdf to Canvas.


## Concept

```{r Q}
#reading check 2
quiz(
  caption = NULL,
  #Q1
  question_multidrop(
  "The following code is in a code chunk: $\\quad 8/2 \\; = 4$",
  choices = c("What is the output?"),
  wordbank = c("4", "TRUE", "FALSE", "NA", "Error", "0"),
  answer(c("Error"), correct = TRUE),
  allow_retry = TRUE,
  incorrect = "submitted"),
  question_blank(
    "In a typical dataframe, columns correspond to ___.",
    answer(c("variables"), correct = TRUE),
    allow_retry = TRUE,
    incorrect = "submitted"
  ),
  question_multidrop(
  "Which of the following shows the relationship between two categorical variables?",
  choices = c(""),
  wordbank = c("linegraph", "faceted histogram", "stacked barplot", "boxplot", "none of these"),
  answer(c("stacked barplot"), correct = TRUE),
  allow_retry = TRUE,
  incorrect = "submitted"
  )

)

```

## Application

Construct a scatterplot of `eruptions` by `waiting` using the `faithful` dataset by filling in the blanks (the data is already preloaded in R).

```{r Ex1, exercise=TRUE}
ggplot(data = faithful, mapping = aes(x = ___, y = ___)) +
  ____
```
